### 2020-02-24 thesis/paper.tex
user done

The first data-set \cite{qcm} includes QCM sensor data where different types of alcohol were passed through the sensor in different concentrations. The task was to find how many types of alcohol were tested and to find the clusters representing each type.
%%img?

@@

The second data-set \cite{wireless} contains signal strenght data from smartphones where the strength of seven nearby wireless networks is collected for each smartphone. The task is to find how many smartphones are in the area of these wireless networks and assign the measurements taken to the smartphones.
%%

@@

The user assumed that those attributes may be Gaussian distributed with possible different distributions and therefor chose the EM clustering algorithm. He sampled the range of $2$ to $5$ for $k$ and calculated $10$ results for each value, to also analyze solutions for different choices of $k$. Next, he changed the threshold in the reachability plot of the meta-view such that visually pleasing solution clusters can be seen. This choice can be seen in Figure \ref{fig:user_iris_optics}.

@@

With this definition he computed consensus results for all groups, which resulted in 3 solutions. As he was told that there are 3 types of flowers the consensus result for the blue meta-cluster was his choice for the final answer, which was also the best overall result. Still, he noted that without this knowledge the choice of two clusters would have been more intuitive for him as the meta-cluster included more results and seemed more robust. The NMI score of his chosen solution was 0.8997 and this clustering solutions is exactly the same as the best single clustering run, this best solution is selected in Figure \ref{fig:user_iris_optics}.

%%

>>>>

The first data-set (QCM3) \cite{qcm} includes QCM sensor data where different types of alcohol were passed through the sensor in different concentrations. The task was to find how many types of alcohol were tested and to find the clusters representing each type.
%%img?

@@

The second data-set \cite{wireless} contains signal strenght data from smartphones where the strength of seven nearby wireless networks is collected for each smartphone. The task is to find how many smartphones are in the area of these wireless networks and assign the measurements taken to the smartphones. The first two dimensions (wifi access-points) can be seen in Figure \ref{fig:user_wifi_gt}, the coloring is according to the ground truth.

\begin{figure}[h]
	\centering
	\includegraphics[scale=.4]{user_wifi_gt}
	\caption{WiFi Localization Data-Set with first two Dimensions shown}
	\label{fig:user_wifi_gt}
\end{figure}

To start of, the user tried creating clustering solutions using DBSCAN, but in both the reachability plot and the heat map it could be seen that no robust solutions except nearly trivial ones could be found. In most cases the points were either nearly all assigned to one cluster or different small clusters each. With this information he deducted, that the algorithm is probably not fit for finding a good solution and chose to use k-means. There, as he did not know how many clusters are in the data-set, he sampled $k$ from $2$ to $50$ and found again that solutions with $k>20$ seemed poor. He decided on this value, just like in the first example, by finding where solutions begin to differ strongly. The resulting reachability plot is shown in Figure \ref{fig:user_wifi_optics}

\begin{figure}[h]
	\centering
	\includegraphics[scale=.5]{user_wifi_optics}
	\caption{OPTICS Plot for WiFi Localization Data-Set}
	\label{fig:user_wifi_optics}
\end{figure}

With the defined meta-clusters, the user used the consensus calculation to obtain the solutions from each meta-cluster. From those, he again chose the result which included the largest number of clusterings in the meta-cluster. This solution can be seen in Figure \ref{fig:user_wifi_consensus}. Again, his reasoning was that as the meta-cluster is largest, the largest number of robust solutions was found in this cluster and therefor most likely combined to the best solution. When looking at the NMI of the found result, the observed value of $0.9142$ is not only very good, it is even higher than the NMI score of the best single clustering run (NMI=$0.8904$). This best simple result can be seen in Figure \ref{fig:user_wifi_best}. Note that the colors of these results are not adapted to best fit the ground truth as it was not available for the user.

\begin{figure}[h]
\centering
\begin{subfigure}[t]{.49\textwidth}
  \centering
  \includegraphics[width=.95\linewidth]{user_wifi_consensus}
  \caption{Consensus Result for blue (largest) Meta-Cluster}
  \label{fig:user_wifi_consensus}
\end{subfigure}
\hfill
\begin{subfigure}[t]{.49\textwidth}
  \centering
  \includegraphics[width=.95\linewidth]{user_wifi_best}
  \caption{Best Result of single Clustering Run}
  \label{fig:user_wifi_best}
\end{subfigure}

\caption{Clustering results for WiFi Localization Data-Set}
\label{fig:user_wifi}
\end{figure}

These findings once again show that with little knowledge on the data one is able to find very good clustering solutions and even get an accurate estimate for the number of clusters.

@@

The user assumed that those attributes may be Gaussian distributed with possibly different distributions and therefor chose the EM clustering algorithm. He sampled the range of $2$ to $5$ for $k$ and calculated $10$ results for each value, to also analyze solutions for different choices of $k$. Next, he changed the threshold in the reachability plot in the resulting meta-view such that visually pleasing solution groups can be seen. This choice is visualized in Figure \ref{fig:user_iris_optics}.

@@

With this definition he computed consensus results for all groups, which resulted in 3 solutions. As he was told that there are 3 types of flowers the consensus result for the blue meta-cluster was his choice for the final answer, which was also the best overall result. Still, he noted that without this knowledge the choice of two clusters would have been more intuitive for him as the meta-cluster included more results and seemed more robust. The NMI score of his chosen solution was $0.8997$ and this clustering solution is exactly the same as the best single clustering run, this best solution is selected in Figure \ref{fig:user_iris_optics} and shown in Figure \ref{fig:user_iris_best}. Again note that this solution is the same as the one obtained by the consensus function when selecting the result with $3$ clusters.

\begin{figure}[h]
	\centering
	\includegraphics[scale=.4]{user_iris_best}
	\caption{First two dimensions of Clustering Solution for Iris Data-Set}
	\label{fig:user_iris_best}
\end{figure}

This shows that using the consensus function may not result in a better solution than can be found by individual clustering algorithm runs, but at least facilitates choosing the correct one out of them. Even though this solution was available, others were present, which would have been a less good choice.
